BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-06-28 implementation.tex
API Instrumentation Section Outlined

Now let us illustrate the actions being performed during API tracing by analyzing in detail each one of the three components of \textit{Figure 3.4}.

\subsection{APIs Instrumentation}
\subsection{API Analysis before Execution}
\subsection{API Analysis after Execution}

>>>>

Now let us illustrate the actions being performed during API tracing by analyzing in detail each one of the three main blocks of \textit{Figure 3.4}.

\subsection{APIs Instrumentation}

The first step taken towards APIs tracing is APIs instrumentation, i.e. placing analysis routines before and after the APIs' execution. To do this, a specific function was embedded in Blue Pill's image callback (the notion of image callback was previously introduced in Section 3.3.1). Such function, named \texttt{AddAnalysisRoutines}, performs the following actions for every DLL being loaded:

\begin{enumerate} 
\item It inspects the symbol table, i.e. the DLL's exports. To this end, Pin symbol objects (\texttt{SYM}s) are employed, which provide information about function symbols in the applications \cite{Pin}.
\item For every symbol object, it retrieves the corresponding routine (\texttt{RTN}) object. In fact, in Pin a \texttt{RTN} represents a function usually generated by a compiler for a procedural programming language, e.g C \cite{Pin}. To retrieve the aforementioned \texttt{RTN} object, the \texttt{RTN\_FindByAddress} API was utilized, which takes as input a \texttt{RTN} memory address and returns an handle to the found \texttt{RTN}. Such memory address was determined by adding the symbol's RVA (obtained via \texttt{SYM\_Value}) to the lowest image address (fetched through \texttt{IMG\_LowAddress}).  
\item For every routine object, it retrieves the corresponding name via \texttt{RTN\_name} and checks whether or not the API being represented is "known", i.e. a source of information associated to the API exists.

\begin{itemize}
\item If the API is not "known", it adds an analysis routine just before the API's execution, which simply logs the value of a user-specified number of args (four by default), exactly like what happens in NTAPIs tracing.
\item If the API is "known", it adds analysis routines before and after the API's execution, which log detailed information relative to the API, including the arguments' input and output values. 
\end{itemize}

\end{enumerate}

Having given a general outline on how \texttt{AddAnalysisRoutine} works, let us now describe its underlying details.

Source of information description. drltrace vs. pyrebox. Hashmaps vs double hashmap. Structs used to represent library calls.

\subsection{API Analysis before Execution}
\subsection{API Analysis after Execution}
